\documentclass{article}
\usepackage{exercise}

\author{
	Dmitrii Galantsev\\
	\texttt{dgalants@iu.edu}
}

\title{REU Personal Statement}

\begin{document}

\maketitle

\section{Why do I want to participate in the Jetstream REU program (what do I hope to gain from this summer research experience)?}
This semester I got very interested in Distributed Systems and its optimization. I have been always amazed with the lower level aspect of Systems in general, and have done research in GPU acceleration as you will see further in this statement. HPC (High Performance Computing) is a continuously growing field and I would like to contribute to the field.

\section{What do I hope to gain from this summer research experience?}
While my interest lies in lower level systems, I'm intrigued to learn a higher level approach. I want to learn how these Distributed Systems could not only be created, but also used and maintained.

\section{What are my short- and long-term career goals?}
While in Indiana University I'm looking to contribute to open source projects and research done on campus or remotely. I'm already contributing to both, more on this in the next answer.\par
After the graduation I'm planning on moving to another state with more demand for CS graduates and possibly work as an Embedded Systems engineer for a few years. After settling down with the job, looking into PhD appears to be a great path.

\section{What are my personal qualities, research, and/or technical skills that are applicable for this research experience?.}
Linux is something that has been part of my life since the end of Middle School. The community and the idea of Open Source are dear to me. Digging through different distributions, and sometimes fully changing my working environment is fun. Of course all under Unix. This comes with a fair amount of Bash and Shell scripting as small scripts have to be written to ease and automate daily usage. Python has been used in my own projects, and in some classes like CSCI-P434 Distributed
Systems (which also introduced me to Matlab).\par
Lots of C had to be written for my classes and personal projects. Last Summer I worked on independent research which covered GPU programming in CUDA C. It ended up being a very involved, demanding project, and I even had to contact one of the CUDA book authors to ask about the upcoming edition.\par
As an addition to my short-term goals, I'm currently working in a Biology lab as an RFID technician. My work consists of updating and upgrading RFID readers which are used for bird data collection and analysis. All of the work is open source and licensed under public domain.\par
I believe all of my previous experiences could be of great use during this summer program. I'm very intrigued to hear back about it.


\end{document}
